\documentclass[UTF-8]{ctexart}
\CTEXsetup[format={\Large\bfseries}]{section}
\usepackage[bottom=3.5cm,top=3.5cm,left=3cm,right=3cm]{geometry}
\title{Postgraduate Research Enhancement Program: How to find and management research literature}
\author{WeijieLi \quad 华南师范大学}
\date{2021.7.15}
\begin{document}
\maketitle
\thispagestyle{empty}
\clearpage

\pagestyle{plain}
\setcounter{page}{1}
\pagenumbering{arabic}

\section{Lecture Summary}
The topic of Professor Wang Fei's lecture is how to find and management research literature.

The first is how to find documents. Commonly used Chinese databases include CNKI and Wanfang, and English databases include Google Scholar, Web of Science and EI (Engineering Index). The school library system usually provides access to the above databases so that students can find materials. It is worth noting that you cannot add redundant keywords when using Google Scholar, otherwise it will have a greater impact on the search results. 

The second is about how to select documents. Professor Wang Fei focused on the points that should be paid attention to when selecting documents in SCI journals. For example, the SCI impact factor (Impact Factor) can reflect the influence of the journal to a certain extent. In addition, partitioning according to SCI can help us search for high-quality documents more quickly. 

Next, Professor Wang Fei introduced several paper management tools to us. For example, Excel (many people did not expect that this commonly used software can also be used to manage papers), endnote, mendeley, Zotero, NoteExpress. The professor used Zotero for a document management demonstration. What you can see is that Zotero is really convenient to use, and I personally prefer to use Zotero. 

Finally, Mr. Wang Fei emphasized the precautions for citing documents when submitting the paper. In fact, I believe everyone has a certain understanding in the graduation project. It should be noted that when submitting the manuscript, it needs to be written in accordance with the standards of the journal, otherwise it is easy to be returned. 

In short, I am very grateful to Professor Wang Fei for his guidance. 


\end{document}