% v2-acmlarge-sample.tex, dated March 6 2012
% This is a sample file for ACM large trim journals
%
% Compilation using 'acmlarge.cls' - version 1.3, Aptara Inc.
% (c) 2011 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
\documentclass[prodmode,acmtap]{acmlarge}

% Metadata Information
\acmVolume{2}
\acmNumber{3}
\acmArticle{1}
\articleSeq{1}
\acmYear{2010}
\acmMonth{5}

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\SetAlFnt{\algofont}
\SetAlCapFnt{\algofont}
\SetAlCapNameFnt{\algofont}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}
\renewcommand{\algorithmcfname}{ALGORITHM}

% Page heads
\markboth{D. Pineo, C. Ware and S. Fogarty}{Neural Modeling of Flow Rendering Effectiveness}

% Title portion
\title{Postgraduate Research Enhancement Program: Postgraduate study, research and career planning}
\author{XuJingxing \affil{South China Normal University}}


\begin{abstract}
Researcher Wang presided over the third lesson of the graduate research promotion plan-how to find and manage research literature. In the lecture, Researcher Wang mainly discussed how to find, select and manage literature.
In terms of searching for literatures, common Chinese databases include CNKI and Wanfang, and English databases include Google Scholar, Web of Science and Engineering Index. When searching for a specific paper, you only need to search for the full name of the paper, but when searching for a certain type of paper, you need to search by keywords.
In terms of selecting literatures, journals are classified into Science Citation Index, Engineering Index and Conference. Professor Wang briefly introduced the impact factor. The impact factor can reflect the influence of a journal to a certain extent. Later, Researcher Wang also demonstrated how to use Web of Science to find papers.
In terms of literature management, it mainly introduces document management software. Common document management software includes Excel, EndNote, Mendeley, Zotero, NoteExpress, etc. Most document management software has the ability to extract document type, author, year, abstract and other information, and also provide some classification and labeling functions. At the end, Researcher Wang also demonstrated how to insert references. The format of references needs to be processed according to the requirements of the journal, so it is also very error-prone.
\end{abstract}

\category{H.5.2}{Information Interfaces and Presentation}{User
Interfaces}[Evaluation/\break methodology]
\category{H.1.2}{Models and Principles}{User/Machine Systems}[Human Information Processing]
\category{I.5.1}{Pattern\break Recognition}{Models}[Neural Nets]

\terms{Human Factors}
\keywords{Contour perception, flow visualization, perceptual theory, visual cortex, visualization}

\acmformat{Daniel Pineo, Colin Ware, and Sean Fogarty. 2010. Neural Modeling of Flow Rendering Effectiveness.}
\begin{document}


\maketitle


\end{document}

