\documentclass[prodmode,acmtap]{acmlarge}

% Metadata Information
\acmVolume{2}
\acmNumber{3}
\acmArticle{1}
\articleSeq{1}
\acmYear{2010}
\acmMonth{5}

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\SetAlFnt{\algofont}
\SetAlCapFnt{\algofont}
\SetAlCapNameFnt{\algofont}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}
\renewcommand{\algorithmcfname}{ALGORITHM}

% Page heads
\markboth{D. Pineo, C. Ware and S. Fogarty}{Neural Modeling of Flow Rendering Effectiveness}

% Title portion
\title{Postgraduate Research Enhancement Program: The introduction of scientific research applications.}
\author{WeijieLi \affil{South China Normal University}}


\begin{abstract}



\end{abstract}



\begin{document}

\maketitle

The last lecture was hosted by Professor Pan Jiahui. The topic of the lecture is the introduction of scientific research applications.

First of all, Professor Pan took the application form of the National Natural Science Foundation of China as an example. Explained several core modules of the declaration form. Many modules are very similar in name. But their emphasis is completely different. Professor Pan gave a detailed explanation. In fact, the quality of the application directly affects whether the project can be approved. The importance of the declaration is self-evident.


Next, Professor Pan introduced the "5W2H" method of writing the declaration. The complete keywords are where, what, why, who, when, how, how much. Working around these seven questions can clearly show the core content of the project on the declaration. Professor Pan used the example of making dumplings to convey a truth. What experts want to see is the results of the project (that is making good dumplings). It is not about the details of the project work (you need to make dumplings yourself). So whether it is the title, or the abstract, or any other part. All should clearly convey the core points. Of course, this does not mean that the research foundation is not important. Some of the team members must have achieved some research results so that they can persuade the judges more effectively.

The major modules do not exist independently, and the major modules provide theoretical support for each other. Finally, it constitutes a complete scientific research application. 

Finally, I would like to thank the teachers for taking the time to hold an introduction lecture on scientific research for us. I believe that the students will gain a lot from this series of lectures. 


\end{document}
% End of v2-acmlarge-sample.tex (March 2012) - Gerry Murray, ACM
