\documentclass[prodmode,acmtap]{acmlarge}

% Metadata Information
\acmVolume{2}
\acmNumber{3}
\acmArticle{1}
\articleSeq{1}
\acmYear{2010}
\acmMonth{5}

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\SetAlFnt{\algofont}
\SetAlCapFnt{\algofont}
\SetAlCapNameFnt{\algofont}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}
\renewcommand{\algorithmcfname}{ALGORITHM}

% Page heads
% \markboth{D. Pineo, C. Ware and S. Fogarty}{Neural Modeling of Flow Rendering Effectiveness}

% Title portion
\title{Postgraduate Research Enhancement Program: Postgraduate study, research and career planning}
\author{XuJingxing \affil{South China Normal University}}


\begin{abstract}
Professor Liang presided over the first lesson of the 2021 graduate research promotion plan-the study, research and career planning of graduate students. In the lecture, Professor Liang mainly discussed the difference between postgraduates and undergraduates, how to study and research, and how to make postgraduate careers more fulfilling.\par
First of all, the task of graduate students is different from that of undergraduates in that the task of undergraduates is learning and application, while the task of graduate students is research and innovation. In order to produce innovative results, graduate students need to cultivate their own research and innovation capabilities.\par
Secondly, the primary task of learning and research is to read the literature. Reading a lot of literature and monographs in this subject and interdisciplinary is the foundation of research and innovation. In the initial stage of research, we can read the review paper first and then the monograph, and we can read the Chinese paper first and then the English paper. In the in-depth research stage, English literature should be mainly read, and the literature with high number of citations, high impact factors and relatively new ones should be given priority. During the reading of the paper, we should pay attention to summarizing the innovative points in the paper, and reproduce the paper as much as possible if conditions permit.\par
Finally, formulate the three-year general goal and annual small goals for graduate students, such as a project, an SCI paper, a competition, and participation in undergraduate guidance work. I personally think that the goal setting is not only related to graduation conditions, but also needs to be combined with one's future development direction (work, Ph.D. or entrepreneurship).\par
I hope I can find my interested and suitable research direction as soon as possible in the process of reading papers and learning technology in the summer.

\end{abstract}

\category{H.5.2}{Information Interfaces and Presentation}{User
Interfaces}[Evaluation/\break methodology]
\category{H.1.2}{Models and Principles}{User/Machine Systems}[Human Information Processing]
\category{I.5.1}{Pattern\break Recognition}{Models}[Neural Nets]

\terms{Human Factors}
\keywords{Contour perception, flow visualization, perceptual theory, visual cortex, visualization}

\acmformat{Daniel Pineo, Colin Ware, and Sean Fogarty. 2010. Neural Modeling of Flow Rendering Effectiveness.}
\begin{document}


\maketitle


\end{document}
% End of v2-acmlarge-sample.tex (March 2012) - Gerry Murray, ACM
